Clause Size Reduction with \alluip Learning

### 2020-05-11 paper.tex
fix a typo
fix a typo, simplify the description of cadical

After the call to \tryuiplevel a check (line~\ref{ln:earlyTerminate})
is made to see if we can abort further processing. At this point the
algorithm has finished processing levels $\dlevels[0]$--$\dlevels[i]$
so the literals at those levels will change. Furthermore, we know that
the best that can be done from this point on is to reduce the
remaining $|\dlevels| - (i+1)$ levels down to a single literal
each. Hence, adding these two numbers gives a lower bound on the size
of the final computed clause. If that lower bound is as large as the
size of the initial \oneuip clause we can terminate and return the initial
\oneuip clause.

@@

$\defaultcadical$ with \oneuip solved 249 instances, 5 more than the result from the SAT 2019 Race.  Applying $\allUipAct$ and $\allUipIn$ further improved the solved instance by 3 an 2, respectively.  The average learnt clause size of \oneuip on $\defaultcadical$ is much larger than other solvers' (101 vs 60) while the average clause size of $\stablealluip$ configurations are similar on all solvers.

>>>>

After the call to \tryuiplevel a check (line~\ref{ln:earlyTerminate})
is made to see if we can abort further processing. At this point the
algorithm has finished processing levels $\dlevels[0]$--$\dlevels[i]$
so the literals at those levels will not change. Furthermore, we know that
the best that can be done from this point on is to reduce the
remaining $|\dlevels| - (i+1)$ levels down to a single literal
each. Hence, adding these two numbers gives a lower bound on the size
of the final computed clause. If that lower bound is as large as the
size of the initial \oneuip clause we can terminate and return the initial
\oneuip clause.

@@

$\defaultcadical$ with \oneuip solved 249 instances,   
and $\allUipAct$ and $\allUipIn$ solved 2 and 3 more instance, respectively.  
The average learnt clause size of \oneuip on 
$\defaultcadical$ is much larger than other solvers' (101 vs 60) 
while the average clause size of $\stablealluip$ configurations are similar on all solvers.
